Towards Pandemic-Scale Ancestral Recombination Graphs of SARS-CoV-2

### 2023-05-26 paper.tex

In this section we focus on the detailed genealogy of samples that have been
previously identified as recombinants, i.e. given a Pango designation that
starts with an ``X''. We focus primarily on the Long ARG in this section,
since it contains many more recombinants; the status
of Pango X lineages in the Wide ARG is briefly summarised in Section~\ref{sec-pango_x_wide_arg}.

>>>>

In this section we focus on the detailed genealogy of samples that have been
previously identified as recombinants, i.e. given a Pango designation that
starts with an ``X''. We focus primarily on the Long ARG
since it contains many more recombinants. The status
of Pango X lineages in the Wide ARG is briefly
summarised in Section~\ref{sec-pango_x_wide_arg}.
